Annotated example of index standardization with VAST

### 2021-11-24 doc/appendix-pcod-VAST.Rmd
Shrink fig

```{r plot-index, echo = TRUE}
if (file.exists(here("doc", "appendix-VAST", "Index-Biomass.png"))) {
  knitr::include_graphics(here("doc", "appendix-VAST", "Index-Biomass.png"))
}
if (file.exists(here("doc", "appendix-VAST", "Index.png"))) {
  knitr::include_graphics(here("doc", "appendix-VAST", "Index.png"))
}
```

>>>>

```{r plot-index, echo = TRUE, out.width="3in"}
if (file.exists(here("doc", "appendix-VAST", "Index-Biomass.png"))) {
  knitr::include_graphics(here("doc", "appendix-VAST", "Index-Biomass.png"))
}
if (file.exists(here("doc", "appendix-VAST", "Index.png"))) {
  knitr::include_graphics(here("doc", "appendix-VAST", "Index.png"))
}
```
